Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-06-10 report/report.tex
Updated LOD summary

Another crucial concept in city modelling is the Level Of Detail (LOD) aspect.
\textbf{(Biljecki, Ledoux and Stoter, 2016 (1))} provide an extensive overview of the concept of LOD in GIS mapping.
They provide the GityGML definition of LOD as a series of different 3D representation of the same data, at different detail levels, and the LOD chosen for a particulary application suggests how the data has been aqquired and modelled.
The CityGML standard divides the LOD representation of 3D models into three classes: A B and C.
\begin{enumerate}
    \item LOD-A models are renderings of the building footprint itself, or rectangular building blocks that have been extruded from the footprint to give the building height.
    \item LOD-B models are building blocks with simplifed roof shapes.
    \item LOD-C models are LOD-B models which include features such as doors, windows, alcoves, building decor, indoor features or vegetation.
\end{enumerate}
A modeler may chose what LOD class(es) to use depending on data availablity and application.

%TODO: Summarize both sources by Biljecki
\textbf{Biljecki, Ledoux and Stoter, 2016 (1)}
\textbf{Biljecki et al, 2014}

>>>>

Another crucial concept in city modelling and GIS mapping is the Level Of Detail (LOD) aspect.
The LOD defines a number of possible different representation of the same GIS data, that vary in the amount of detail in its presentation.
A modeler can choose to present the same data (e.g. building, roads, or decorative models) at different detail levels, depending on the use and application.
Furthermore, the LOD chosen for a particulary application also suggests how the data has been aqquired and modelled.
It turns out however, in practise, that the terminology and use of LOD is still ambigous and the definitions vary greatly between practitioners, standards and institutions, despite its usefulness.
\textbf{(Biljecki et al, 2014)}

\textbf{(Biljecki, Ledoux and Stoter, 2016 (1))} provide the GityGML definition of LOD.
The CityGML standard divides the LOD representation of 3D models into three classes: A B and C.
\begin{enumerate}
    \item LOD-A models are renderings of the building footprint itself, or rectangular building blocks that have been extruded from the footprint to give the building height.
    \item LOD-B models are building blocks with simplifed roof shapes.
    \item LOD-C models are LOD-B models which include features such as doors, windows, alcoves, building decor, indoor features or vegetation.
\end{enumerate}
A modeler may chose what LOD class(es) to use depending on data availablity and application.
